---
output:
  html_notebook: default
  html_document: default
---
# Recommendation Engine

### Problem Statement :- 

  - Build a recommender system with the given data using UBCF.

### Data Understanding

```{r}
rating <- read.csv("~/desktop/Digi 360/Module 16/Archive-4/movie.csv")
head(rating)
```

### Importing the libraries

```{r}
library("recommenderlab")
library(caTools)
```

```{r}
#metadata about the variable
str(rating)
```

### Data Visualization

```{r}
#rating distribution
hist(rating$rating)
```



```{r}
#the datatype should be realRatingMatrix inorder to build recommendation engine
rating_matrix <- as(rating, 'realRatingMatrix')
```

```{r}
rating_matrix
```


### Heatmap of Movie Ratings

```{r}
image(rating_matrix[1:10, 1:10], axes = FALSE, main = "Heatmap of the first 10 rows and 10 columns")
```

### Building Model

#### User Based Collaborative Filtering

```{r}
movie_recomm_model <- Recommender(rating_matrix, method="UBCF")
```

### Predictions

```{r}
#Predictions for two users 
recommended_items <- predict(movie_recomm_model, rating_matrix[1000], n=5)
as(recommended_items, "list")
```

### Conclusion:- 

  - For the user 1000, the top recommended movies are:- 
  
    "Sabrina (1995)"           
    "Waiting to Exhale (1995)"
    "Sudden Death (1995)"      
    "Tom and Huck (1995)"
